---
title: "Iris Data Set Shiny Application"
author: "Ella S."
date: "February 10, 2016"
output: html_document
---


##Purpose
The purpose of this application is to demonstrate different features of the shiny framework by Rstudio.

This web application is based on the [famous Iris data set](https://stat.ethz.ch/R-manual/R-devel/library/datasets/html/iris.html) 

Inspired from the  
[shiny gallery example](http://shiny.rstudio.com/gallery/kmeans-example.html)

```{r}
head(iris)
levels(iris$Species)
```


##What it does
This application takes the Iris data set and runs a simple regression model for the different parameters 
that  are choosen from the web interface. 


The are  3 Tabs : ***Plot/Summary/Photo***

* **Plot** -  plots the x, y  relation according to different Iris species and also plots the relation for all species.

    x,y axes can be choosen from dropdown lists, which are the Iris flower features 

```{r}
plot(x = iris$Sepal.Length, y = iris$Sepal.Width, pch=20,cex=3,col=iris$Species)
```

* **Summary** - summary for the regression model 
```{r}
   summary(lm(iris$Sepal.Width ~ iris$Sepal.Length))
```

* **Photo** - this tab includes  the picture for each Iris species  from Wikipedia

## Usage
1) Choose the  Iris species from the radio box
2) Choose the x, y axes from the dropdown lists 
3) Navigate  to Summary tab to see the regression model results
4) Navigate to Photo tab to view Iris picture
5) Choose different options for each tab 





